Online cassification of ArXiv papers based on your preferences

### 2014-05-19 Presentation.tex
Modified presentation and added Readme.

\begin{frame}
\frametitle{Method}
\begin{itemize}
\item Start: simple perceptron and bag-of-words model.
\item Update always when  $\hat{y} = 1$, and with probability $p$ if $\hat{y} = -1$.
\item Can show that this achieves a bound on mistakes in expectation similar to normal perceptron $E[M] \leq \frac{1}{p}\frac{r^2}{\rho^2}$.
\item Much weaker bound, but requires less ``work'' from the user.
\item Intuitively, maybe we should look at more of the $\hat{y} = -1$ observations when we're less sure of the algorithm.
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item Start with $p = 1$, increase $p$ on false negatives, decrease $p$ on correct negative predictions.
\item Never reduce $p$ below some value $p_\min$. 
\item Set $p = p + \gamma_1(1 - p)$ when we're wrong, and $p = p - \gamma_2(p - p_\min)$ when correct.
\item Can show the same bound holds as in the constant $p$ case, using $p = p_\min$.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Results}
We each labeled several articles, shuffled their order, and then tested several online learning algorithms on them.  We measured recall and number of negative labels required in the last 120 papers.
\includegraphics[width=0.6\textwidth]{EveryoneRecallPaper.pdf}
\end{frame}

>>>>

\begin{frame}
\frametitle{Method}
\begin{itemize}
\item Start: simple perceptron and bag-of-words model.
\item Update always when  $\hat{y} = 1$, and with probability $p$ if $\hat{y} = -1$.
\item Can show that this achieves a bound on mistakes in expectation similar to normal perceptron $\mathbb{E}[M] \leq \frac{1}{p}\frac{r^2}{\rho^2}$.
\item Much weaker bound, but requires less ``work'' from the user.
\item Intuitively, maybe we should look at more of the $\hat{y} = -1$ observations when we're less sure of the algorithm.
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item Start with $p = 1$, increase $p$ on false negatives, decrease $p$ on correct negative predictions.
\item Never reduce $p$ below some value $p_\min$. 
\item Set $p = p + \gamma_1(1 - p)$ when we're wrong, and $p = p - \gamma_2(p - p_\min)$ when correct.
\item Can show the same bound holds as in the constant $p$ case, using
  $p = p_\min$. $\mathbb{E}[M] \leq \frac{1}{p_{\min}}\frac{r^2}{\rho^2}$.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Results}
We each labeled several articles, shuffled their order, and then
tested several online learning algorithms on them.  We measured recall
and number of labels used by the algorithm when $\hat{y} = -1$.
\begin{figure}
\centering
\includegraphics[width=0.7\textwidth]{EveryoneRecallPaper.pdf}
\end{figure}
\end{frame}
